\beginsong{Hit the road Jack}[wuw={Ray Charles}]

\beginverse*
\[Am] \[G] \[F] \[E7]
\[Am] \[G] \[F] \[E7]
\endverse

\beginchorus
Hit the \[Am]road \[G]Jack and\[F] don't you come \[E7]back \[Am]no more, \[G]no more, \[F]no more, \[E7]no more.
Hit the \[Am]road \[G]Jack and\[F] don't you come \[E7]back no \[Am]more\[G]. \[F](W\[E7]hat you say?)
Hit the \[Am]road \[G]Jack and\[F] don't you come \[E7]back \[Am]no more, \[G]no more, \[F]no more, \[E7]no more.
Hit the \[Am]road \[G]Jack and\[F] don't you come \[E7]back no \[Am]more\[G].\[F]\[E7]
\endchorus

\beginverse
Oh \[Am]woman, oh \[G]woman, don't \[F]treat me so \[E7]mean,
You're the \[Am]meanest old \[G]woman that I've \[F]ever \[E7]seen.
I \[Am]guess if \[G]you say \[F]so\[E7]
I'll \[Am]have to pack my \[G]things and \[F]go. (That's \[E7]right)
\endverse

\printchorus

\beginverse
Now b\[Am]aby, listen ba\[G]by, don't-a t\[F]reat me this-a \[E7]way
For I'\[Am]ll be \[G]back on my fe\[F]et some da\[E7]y.
(Don't\[Am] care if you \[G]do 'cause it's \[F]underst\[E7]ood
you ain't \[Am]got no mon\[G]ey you ju\[F]st ain't no g\[E7]ood.)
Well, I g\[Am]uess if y\[G]ou say \[F]so\[E7]
I'd h\[Am]ave to pack my \[G]things and \[F]go. (That's \[E7]right)
\endverse

\printchorus

\beginverse*
D\[F]on't you \[E7]come back no more.
\[Am](aah! what you\[G] say)            D\[F]on't you \[E7]come back no more.
\[Am](I didn't unde\[G]rstand you)      D\[F]on't you \[E7]come back no more.
\[Am](You can't mea\[G]n that)          D\[F]on't you \[E7]come back no more.
\[Am](Oh, now baby,\[G] please)         D\[F]on't you \[E7]come back no more.
\[Am](What you tryi\[G]n' to do to me?) D\[F]on't you \[E7]come back no more.
\[Am](Oh, don't tre\[G]at me like that) D\[F]on't you \[E7]come back no more.
\endverse

\endsong
