\beginsong{Rawhide}[wuw={The Blues Brothers}]

\beginverse*
\[Am]Rollin' Rollin' Rollin'  (x4)
Rawhide
\endverse

\begin{minipage}{.85\textwidth}%
\beginverse
R\[Am]ollin' Rollin' Rollin', though the streams are swollen
k\[C]eep them dogies rollin', Rawhide!
R\[Am]ain and wind and weather, h\[Dm]ell b\[G]ent for lea\[Am]ther,
w\[G]ishin' my g\[F]al was by my si\[E]de.
\[Am]All the things I'm missin', good v\[Dm]ittles, l\[G]ove and k\[Am]issin',
are wa\[Dm]itin' at the \[Am]end \[G]of my \[Am]ride.
\endverse

\beginchorus
Move 'em\[Am] on, head 'em up, h\[E]ead 'em up, move 'em on,
mov\[Am]e 'em on, head 'em up, Ra\[E]whide!
Cut 'em o\[Am]ut, ride 'em in, r\[E]ide 'em in, cut 'em out,
\[Am]cut 'em out, \[E]ride 'em \[F]in, \[E7]Rawh\[Am]ide!
\endchorus

\end{minipage}%
\begin{minipage}{.15\textwidth}
	\vspace{0pt}
    \begin{flushright}
    \hfill\gtab{Db}{X43121:043020} 
    \hfill\gtab{Ebm}{XX1342:001342}
    \hfill\gtab{Ab}{4:134211:034200}
    \hfill\gtab{Gb}{2:134211:034200}
    \end{flushright}
\end{minipage}%



\beginverse
keep m\[Bbm]ovin' movin' movin', though they are disapprovin'
\[Db]keep them dogies movin', Rawhide!
Don't t\[Bbm]ry to understand them, just \[Ebm]rope, th\[Ab]row and b\[Bbm]rand 'em,
s\[Ab]oon we'll be \[Gb]livin' high and \[F]wide.
\[Bbm]My heart's calculatin', my t\[Ebm]rue love w\[Ab]ill be wa\[Bbm]itin',
be wa\[Ebm]itin' at the \[Bbm]end \[Ab]of my \[Bbm]ride.
\endverse

\beginchorus
Move 'em\[Bbm] on, head 'em up, he\[F]ad 'em up, move 'em on,
mov\[Bbm]e 'em on, head 'em up, Ra\[F]whide!
Cut 'em o\[Bbm]ut, ride 'em in, ri\[F]de 'em in, cut 'em out,
\[Bbm]cut 'em out, ride '\[F]em \[Gb]in, R\[F7]awh\[Bbm]ide!
\endchorus

\beginverse*
\[Bbm] \[Bbm] \[Db] \[Db]
\[Bbm] \[Ebm] \[Ab] \[Bbm] \[Ebm] \[Bbm] \[Ab] [Bbm]
\endverse

\beginchorus
Move 'em\[Bbm] on, head 'em up, he\[F]ad 'em up, move 'em on,
mov\[Bbm]e 'em on, head 'em up, Ra\[F]whide!
Cut 'em o\[Bbm]ut, ride 'em in, ri\[F]de 'em in, cut 'em out,
\[Bbm]cut 'em out, ride '\[F]em \[Gb]in, R\[F7]awh\[Bbm]ide!
\endchorus

\beginverse*
\[Bbm]Rollin' Rollin' Rollin'  (x4)
Rawhide
\endverse

\endsong
