\beginsong{Welcome To The Internet}[wuw={Bo Burnham}]

\beginverse
\[Dm]Welcome to the internet. Have a look around.
\[Gm]Anything that brain of yours can think of can be found.
We've got \[F]mountains of content. Some better, some worse.
If \[A7]none of it's of interest to you, you'd be the first.
\endverse

\beginverse
\[Dm]Welcome to the internet. Come and take a seat.
Would you \[Gm]like to see the news or any famous women's feet.
There's \[F]no need to panic. This isn't a test (huh huh).
J\[A7]ust nod or shake your head and we'll do the rest.
\endverse

\beginverse
\[Dm]Welcome to the internet. What would you prefer.
Would you \[Gm]like to fight for civil rights or tweet a racial slur.
Be \[F]happy. Be horny. Be bursting with rage.
\[A7]We got a million different ways to engage
\endverse

\beginverse
\[Dm]Welcome to the internet. Put your cares aside.
Here's a \[Gm]tip for straining pasta. Here's a nine-year-old who died.
We got \[F]movies, and doctors, and fantasy sports.
And a \[A7]bunch of colored pencil drawings of all the characters of harry potter fucking \[Dm]eachother.
\endverse

\beginverse
Welcome to the internet. Hold on to your socks.
'cause a \[Gm]random guy just kindly sent you photos of his cock.
They are \[F]grainy and off-putting. He just sent you more.
\[A7]Dont act surprised. You know you like it, you whore.
\endverse

\beginverse
\[Dm]See a man beheaded. Get offended, see a shrink.
Show us \[Gm]pictures of your children. Tell us every thought you think.
Start a \[F]rumor, buy a broom or send a death threat to a boomer.
Or \[A7]DM a girl and groom her. Do a Zoom or find a tumor in your-
\endverse

\beginverse
\[Dm]Here's a healthy breakfast option. You should kill your mom.
Here's why \[Gm]women never fuck you. Here's how you can build a bomb.
Which \[F]Power Ranger are you? Take this quirky quiz.
O\[A7]bama sent the immigrants. To \[A7]vac- \[Gm]cin- \[F]ate- \[E]your- \[Dm]kids.
\endverse

\beginchorus
Could I i\[Dm]nterest you in everything, all of the time?
A \[Gm]little bit of everything. All of the time.
\[F]Apathy's a tragedy and boredom is a crime.
\[A7*]Anything and everything. All of the time.
Could I i\[Dm]nterest you in everything, all of the time?
A \[Gm]little bit of everything. All of the time.
\[F]Apathy's a tragedy and boredom is a crime.
\[A7*]Anything and everything. All of the time.
\endchorus

\beginverse
{\nolyrics Interlude \[Dm]\[C]\[Bb]\[A7]}
\endverse

\beginverse
\[Dm]You know, \[C]it wasn't always like \[Bb]this\[A7]
\[Dm]Not very \[C]long ago
\[Bb]Just before your \[A7]time
\[Dm]Right before \[C]the towers fell
\[Bb]Circa '99\[A7]
\endverse

\beginverse
This was \[Gm]catalogues
T\[Dm]ravel blogs
\[A7]A chat room or \[Dm]two
We set our s\[Gm]ights and \[Dm]spent our nights
\[A7]Waiting\[C7]
\endverse

\beginverse
For \[Fmaj7]you
\[Dm7]You
In\[Gm7]satiable \[C7]you
Mommy \[Fmaj7]let you use her i\[Dm7]Pad
\[Gm7]You were barely \[C7]two
And it \[Dm]did all the \[Dmmaj7/C#]things
We \[Dm7/C]designed it to \[Bb]do
\endverse

\beginverse
Now \[Bb]look at you
Oh, \[C]look at you
\[D]You
\endverse

\beginverse
\[Gmaj7]You\[Em7]
Un\[Am7]stoppable, w\[D7]atchable
Your \[Gmaj7]time is now. Your i\[Em7]nside's out.
\[Am7]Honey, how you \[D7]grew
And if \[Em]we stick to\[Emmaj7/D#]gether
Who \[Em7/D]knows what we'll \[A]do
It was \[C]always the pl\[D]an
To put the \[B7]world in your h\[C]and
\[Em](la\[Em/B]ughin\[Em]g)\[Em/B]\[Em]\[Em/B]\[Em]\[Em/B]
\endverse


\beginchorus
Could I i\[Em]nterest you in everything, all of the time?
A \[Am]bit of everything. All of the time.
\[G]Apathy's a tragedy and boredom is a crime.
\[B7*]Anything and everything. All of the time.
Could I i\[Em]nterest you in everything, all of the time?
A \[Am]little bit of everything. All of the time.
\[G]Apathy's a tragedy and boredom is a crime.
\[B7]Anything and everything
\[B7]And anything and everything
\[B7]And anything and everything
And \[N.C.]all of the time
\endchorus


\endsong
